Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2023-01-27 RR_manuscript/RR.tex
♻️ - render RR and RR diff

The results section is divided into three parts.
We first provide a statistical description of team composition, nature of acoustic analyses and statistical approaches, and peer-review ratings.
Second, we report the results of the meta-analytic model, focusing on between-team and between-model variability.
Finally, we present the analysis of the effect of analytic and researcher-related predictors on the meta-analytic effect.
The research compendium of the study, containing all the code and data presented here, can be found in the GitHub repository linked in the research compendium at \url{https://osf.io/3bmcp/}, in the \texttt{scripts/r/} folder.

@@

Our quantitative assessment did not include other degrees of freedom, all of which are additional sources of variation:
Teams differed with regard to how the acoustic signal was segmented ranging from fully automated forced-alignment with minimal manual correction to complete manual alignment performed by the analysts; teams differed in whether the statistical analysis was based on a subset of the data or the whole dataset; and they differed whether and if so how measurements were excluded based on both qualitative (i.e.~whether specific speech production instances were excluded or not) and quantitative grounds (i.e.~whether data were trimmed or not).

>>>>

The results section is divided into three parts.
We first provide a statistical description of team composition, nature of acoustic analyses and statistical approaches, and peer-review ratings.
Second, we report the results of the meta-analytic model, focusing on between-team and between-model variability.
Finally, we present the analysis of the effect of analytic and researcher-related predictors on the meta-analytic effect.
The research compendium of the study, containing all the code and data presented here, can be found in the GitHub repository linked in the research compendium at \url{https://osf.io/3bmcp/}, in the \texttt{scripts/r/} folder.
An interactive web application that allows the interested reader to explore the data set is available at \url{https://many-speech-analyses.github.io/shiny}.

@@

Our quantitative assessment did not include other degrees of freedom, all of which are additional sources of variation:
Teams differed with regard to how the acoustic signal was segmented ranging from fully automated forced-alignment with minimal manual correction to complete manual alignment performed by the analysts; teams differed in whether the statistical analysis was based on a subset of the data or the whole data set; and they differed whether and if so how measurements were excluded based on both qualitative (i.e.~whether specific speech production instances were excluded or not) and quantitative grounds (i.e.~whether data were trimmed or not).
